---
output:
  pdf_document: default
  html_document: default
---
---
title: "DSCC/CSC/STAT 462 Assignment 4 - Aradhya Mathur"
output:
  pdf_document: default
  html_document:
    df_print: paged
subtitle: Due November 3, 2022 by 11:59 p.m.
fontsize: 12pt
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, eval=T,tidy=TRUE, tidy.opts=list(width.cutoff=60))
```
  
\vspace{5pt}
Please complete this assignment using `RMarkdown`, and submit the knitted PDF. *For all hypothesis tests, state the hypotheses, report the test statistic and p-value, and comment on the results in the context of the problem.* 
\vspace{5pt}

1. Recall the "airbnb.csv" dataset from HW3. Data collected on $n=83$ Air BnB listings in New York City are contained in the file "airbnb.csv." Read this file into R and, just as in HW3, create two new variables, one for the price of full house rentals and one for the price of private room rentals. (It may be useful to revisit some of your code from that assignment.)
```{r}
air <-  read.csv('airbnb.csv.')
head(air)
home <- air[air$room_type=='Entire home', ]
price_home = home$price
price_home
private <- air[air$room_type=='Private room', ]
price_private = private$price
price_private
```


    a. At the $\alpha=0.05$ level, test "by-hand" (i.e. do not use any `.test()` function, but still use `R`) whether the variance of price of entire home rentals is significantly different from the variance of price of private home rentals. 
    H0: var of price of entire home equal to var of price of private room
    H1: var of price of entire home not equal to var of price of private room
    
```{r}
sdhome = sd(price_home)
n1 = 27
sdhome
sdprivate = sd(price_private)
n2 = 56
sdprivate
f = (sdhome^2)/(sdprivate^2)
f
pval = 2*(1-pf(f,n1-1,n2-1))
pval
```
    P val = 0 which is less than alpha so we reject the null hypothesis
    
    
    b. At the $\alpha=0.05$ level, test "by-hand" (i.e. do not use any `.test()` function, but still use `R`) whether the variance of price of private room rentals is significantly different from $40^2$. 
\vspace{10pt}

H0: variance of price of private room rentals is = $40^2$
h1: variance of price of private room rentals is significantly different from $40^2$

```{r}
fnew = (n2-1)*(sdprivate^2)/(40*40)
fnew
pval = 2*(1-pchisq(fnew,55))
pval
```
P val is less than alpha (reject null hypothesis) so it is significantly different.

2. A gaming store is interested in exploring the gaming trends of teenagers. A random sample of $143$ teenagers is taken. From this sample, the gaming store observes that 95 teenagers play videos games regularly. For all parts of this problem, do the calculation "by-hand" (i.e. do not use the `prop.test()` or `binom.test()` functions, but still use `R`).

    a. Construct a two-sided (Wald) 95% confidence interval for the proportion of all teenagers who play video games regularly. Interpret the interval.
    
```{r}
x = 95
n = 143
pcap = x/n
pcap
z1 = qnorm(0.975)
z1

funct = sqrt((pcap*(1-pcap))/n)
funct
interval = z1*funct
interval
lower = pcap - interval
lower
upper = pcap + interval
upper

```
    (0.5869382,0.7417331) is the a two-sided (Wald) 95% confidence interval for 
    the proportion of all teenagers who play video games regularly
    
    
```{r}
#prop.test(x=95, n=143, p = NULL,
 #         alternative = c("two.sided", "less", "greater"),
  #        conf.level = 0.95, correct = TRUE)
```
    
    
    b. A teen magazine advertises that "74% of teenagers play video game regularly," and you want to see if this claim is true. Perform a hypothesis test at the $\alpha=0.05$ significance level to test whether this claim is correct.
    
  H0: 74% people play regularly
  H1: 74% people dont play regularly
    
```{r}
pn = 0.74
deno = sqrt((pn*(1-pn))/n)
deno
zb = (pcap-pn)/deno
zb
pval = 2*(pnorm(zb))
pval
```
    P value is less than alpha and we reject H0.
    74% of teenagers don't play video game regularly
    
    
    c. Comment on how comparable the results are from the confidence interval and the hypothesis test in examining the teen magazine's claim. Explain. 
\vspace{10pt}

Both confidence interval and hypothesis test provide the same inference but in 
different manner. If for some percent of teenagers, p value is greater than alpha, 
then for sure for that value will lie between the confidence interval.
Confidence intervals uses data from a sample to estimate a population parameter. 
While, hypothesis tests uses data from a sample to test a specified hypothesis. 

    
3. Researchers at a Las Vegas casino want to determine what proportion of its visitors smoke while in the casino. Casino executives are planning to conduct a survey, and they are willing to have a margin of error of 0.07 in estimating the true proportion of visitors who  smoke. If the executives want to create a two-sided (Wald) 99\% confidence interval, how many visitors must be included in the study?
\vspace{10pt}
```{r}
m = 0.07
p3 = 0.5
z3 = qnorm(0.995)
z3
num3 = ((z3^2)*(p3)*(1-p3))
num3
deno3 = m^2
deno3
n3 = num3/deno3
ans3 = ceiling(n3)
ans3

```
 339 visitors must be included in the study.
 

4. Are people in Australia more likely to have pets than people in America? Of a sample of 51 Australians, 32 indicated having a pet. In an independent sample of 63 Americans, 27 indicated having a pet. Test "by-hand" (i.e. do not use the `prop.test()` or `binom.test()` functions, but still use `R`) at the $\alpha=0.05$ significance level whether the proportion of Australians who have pets is greater than the proportion of Americans who have pets.
\vspace{10pt}

H0: Proportion of Australians who have pets is less than or equal to the 
proportion of Americans who have pets
H1: Proportion of Australians who have pets is greater than the proportion of
Americans who have pets
```{r}
n1 = 51
x1 =32
p1cap = x1/n1
n2 = 63
x2 =27
p2cap = x2/n2
pcap4 = (x1 + x2)/(n1+n2)
pcap4
num4 = p1cap - p2cap
d4 = pcap4*(1-pcap4)
d4_ = (1/n1) + (1/n2)
den4 = d4*d4_
deno4 = sqrt(den4)
z4 = num4/deno4
z4
pval = (1-pnorm(z4))
pval
```
We reject the null hypothesis as pval < alpha


5. Researchers are interested in exploring severity of COVID-19 symptoms by age group. A sample of 193 patients at a health clinic were asked their age and have their symptoms categorized as "asymptomatic," "moderate," or "severe." The results are presented in the table below. Conduct an appropriate test (you do not need to do this test "by-hand" and can use the `chisq.test()` function) at the $\alpha=0.01$ significance level to determine whether severity of COVID-19 symptoms is associated with age. 
\begin{tabular}{c|ccc|c}
  \hline
Age (years) & Asymptomatic & Moderate & Severe & Total\\
   \hline
$[0,18)$ & 22 & 13 & 7 &  42\\
$[18,55)$ & 36 & 22 & 28 & 86 \\
$55$ and older & 10 & 29 & 26 & 65\\
   \hline  
   Total &68 & 64 & 61 & 193\\
\end{tabular}
\vspace{10pt}

```{r}
tab <- matrix(c(22,36,10,13,22,29,7,28,26), nrow = 3, ncol = 3)
tab
```
```{r}
chisq.test(tab,correct = F)
```
From the test we got X-squared = 20.408 
degree of freedom = 4
p-value = 0.0004147


6. A study was conducted to investigate the respiratory effects of sulphur 
dioxide in subjects with asthma. During the study, two measurements were taken 
on each subject. First, investigators measured the increase in specific airway 
resistance (SAR)---a measure of broncho-constriction---from the time when the 
individual is at rest until after he/she has been exercising for 5 minutes 
(variable: `air`). The second measurement is the increase in SAR for the same
subject after he/she has undergone a similar 5 minute exercise conducted in an 
atmosphere of 0.25 ppm sulfur dioxide (variable: `sulf.diox`). Ultimately, we are
interested in examining the `air-sulf.diox` difference. For the 17 subjects
enrolled in the study, the two measurements are presented in dataset "asthma.csv"
on Blackboard.

```{r}
asthma <-  read.csv('asthma.csv')
asthma

```

    a.  At the $\alpha=0.01$ significance level, use a Wilcox signed-rank test "by-hand" (i.e. do not use the `wilcox.test()` function, but still use `R`) to test the null hypothesis that the median difference in increase in SAR for the two air conditions is equal to 0 against the two-sided alternative hypothesis that it is not equal to 0. What do you conclude? Perform this test using a normal distribution approximation.
    
    Ho: Increase equal to zero
    H1: Increase not equal to 0
    
```{r}
asthma$difference = asthma$air-asthma$sulf.diox
asthma$rank = rank(abs(asthma$difference))
asthma
t_plus = 2+6+3+10
t_plus
t_neg = 4+7+1+8+9+11+12+13+5+14+15+16+17
t_neg
t = t_plus - t_neg
t
n = 17
sigm = sqrt(((n)*(n+1)*(2*n+1))/6)
sigm
zt = t/sigm
zt
p_ast = 2*(pnorm(zt))
p_ast
```
    P value (0.008607429) is less than alpha, we reject the null hypothesis.
    
    
    b. Run the test again using the exact signed-ranked distribution (i.e., `wilcox.test()`). How does the p-value differ from the result in part b?
    
```{r}
wilcox.test(asthma$air, asthma$sulf.diox, paired=T, exact=T, correct =F )
```
    P value in the wilcox.test() is less than what we got from part a. But the
    inference is still the same. 
    \vspace{10pt}
    
7. The data in the file "bulimia.csv" are taken from a study that compares adolescents who have bulimia to healthy adolescents with similar body compositions and levels of physical activity. The data consist of measures of daily caloric intake for random samples of 23 bulimic adolescents and 15 healthy adolescents. 
    a. Read the data into R. To do so, use code such as this:
    
    ```{r, eval=F}
    bulimia <- read.csv("bulimia.csv")
    bulimic <- bulimia$bulimic
    healthy <- bulimia$health[1:15]
    healthy
    bulimia
    ```
    b. Test the null hypothesis that the median daily caloric intake of the population of individuals suffering from bulimia is equal to the median caloric intake of the healthy population. Conduct a two-sided test at the $\alpha=0.01$ significance level (you do not need to do this test "by hand"; i.e., you may use a `.test()` function). Use a normal approximation for the distribution of the test statistic. 
    
    H0: median daily caloric intake of the population of individuals suffering 
    from bulimia is equal to the median caloric intake of the healthy population
    H1: median daily caloric intake of the population of individuals suffering from 
    bulimia is not equal to the median caloric intake of the healthy population
    
```{r}
bulimia <- read.csv("bulimia.csv")
bulimic <- bulimia$bulimic
healthy <- bulimia$health[1:15]
n_bul = 23
n_health = 15
wilcox.test(bulimic, healthy, exact = F, correct = F)
```
    P value 0.0005927 is less than alpha so we reject the null hypothesis.
    
  
    
Short Answers:

  * About how long did this assignment take you? Did you feel it was too long, too short, or reasonable? 
  3 hours. Reasonable length
  
  * Who, if anyone, did you work with on this assignment?
  No one
  
  * What questions do you have relating to any of the material we have covered so far in class? 
  F test, Chi Square test, wilcoxon signed rank test